Paper Analyses

### 2022-12-05 PaperAnalyses&Figures.Rmd
Updated plots, updated difference score model (save method)

3 plots: youth-report puberty, parent-report puberty, cognition
```{r}
#Youth-Report Puberty
#make categorical variable for puberty
#age-corrected cognition: These are presented as Standard Scores (mean=100, SD=15).
categorical_pds_baseline <-  brainage_pds_baseline %>% 
  mutate(youth_pds_cat=cut(youth_mean, breaks=c(-Inf, 1, 2, 3, Inf), labels=c("1","2","3", "4")),
         parent_pds_cat=cut(parent_mean, breaks=c(-Inf, 1, 2, 3, Inf), labels=c("1","2","3", "4")),
         cognition_cat=cut(nihtbx_totalcomp_uncorrected, breaks=c(-Inf, 85, 115, Inf), labels=c(">-1", "-1-1", ">1")),
         cognition_cat_small=cut(nihtbx_totalcomp_uncorrected, breaks=c(-Inf, 92, 108, Inf), labels=c(">-.5", "-.5-.5", ">.5")),
         cog_quart = cut(nihtbx_totalcomp_uncorrected, quantile(nihtbx_totalcomp_uncorrected, na.rm=T), labels=c("0-25", "25-50", "50-75", "75-100")))
#don't z-score, include more than 1 standard deviation and less than 1 standard deviation (ignore within 1 SD)

ggpar((categorical_pds_baseline %>% 
  filter(!is.na(youth_pds_cat)) %>% 
  ggdensity(x = "corrected_gap", color= "youth_pds_cat", fill= "youth_pds_cat", add="mean", palette = c('#3E502A','#7CA352','#A1C181', '#CCDDBB'))),  #,'#526D37'
  xlab="Brain Age Gap", ylab="Density", legend.title = "Youth-Report PDS") +
  theme(text = element_text(size = 24)) 
ggsave(filename="baseline_youth_pds_mod1.png",
                          width=7, height=4, units='in', dpi=300)

#Parent-Report Puberty
ggpar((categorical_pds_baseline %>% 
  filter(!is.na(parent_pds_cat)) %>% 
ggdensity(x = "corrected_gap", color= "parent_pds_cat", fill= "parent_pds_cat", add="mean", palette = c('#3E502A','#7CA352','#A1C181', '#CCDDBB'))), 
  xlab="Brain Age Gap", ylab="Density", legend.title = "Parent-Report PDS") +
  theme(text = element_text(size = 24)) 
ggsave(filename="baseline_parent_pds_mod1.png",
                          width=7, height=4, units='in', dpi=300)

@@

#Cognition Quartiles
ggpar((categorical_pds_baseline %>% 
  filter(!is.na(cog_quart) & cog_quart!="25-50" & cog_quart!="50-75" ) %>% 
  ggdensity(x = "corrected_gap", color= "cog_quart", fill="cog_quart", add="mean", palette = c('#7CA352',
 '#CCDDBB'))), xlab="Brain Age Gap", ylab="Density", legend.title = "Cognition (Quartiles)")  +
  theme(text = element_text(size = 24)) 
ggsave(filename="baseline_cognition_mod1.png",
                          width=7, height=4, units='in', dpi=300)

@@

ggplot(brainage_pds_baseline, aes(x=truth, y=corrected_pred)) + 
  geom_jitter(color="#A1C181")+
  geom_abline(a=0, b=1, color='#233D4D') +
  #geom_smooth(method=lm, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Predicted Age", title = "Age v Pred Age - Model 1 (Baseline)") +
  theme_classic() + 
  theme(text = element_text(size = 22))  
ggsave(filename="baseline_truth_corrected_pred_mod1.png",
                          width=7, height=4, units='in', dpi=300)

@@

ggplot(brainage_pds_baseline, aes(x=truth, y=corrected_gap)) + 
  geom_jitter(color="#A1C181")+
  geom_smooth(method=lm, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Corrected Gap", title = "Age Bias - Model 1 (Baseline)") +
  theme_classic() + 
  theme(text = element_text(size = 22))  
ggsave(filename="baseline_truth_corrected_gap_mod1.png",
                          width=7, height=4, units='in', dpi=300)
```

@@

ggplot(brainage_pds_followup, aes(x=truth, y=corrected_pred)) + 
  geom_jitter(color="#619B8A")+
  geom_abline(a=0, b=1, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Predicted Age", title = "Age v Pred Age - Model 1 (Follow-Up)") +
  theme_classic() + 
  theme(text = element_text(size = 22))  
ggsave(filename="followup_truth_corrected_pred_mod1.png",
                          width=7, height=4, units='in', dpi=300)

# Age Bias - truth vs corrected gap
ggplot(brainage_pds_followup, aes(x=truth, y=corrected_gap)) + 
  geom_jitter(color="#619B8A")+
  geom_smooth(method=lm, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Corrected Gap", title = "Age Bias - Model 1 (Follow-Up)") +
  theme_classic() + 
  theme(text = element_text(size = 22))  
ggsave(filename="followup_truth_corrected_gap_mod1.png",
                          width=7, height=4, units='in', dpi=300)

@@

@@

ggpar((categorical_pds_followup %>% 
  filter(!is.na(youth_pds_cat)) %>% 
  ggdensity(x = "corrected_gap", color= "youth_pds_cat", fill= "youth_pds_cat", add="mean", palette=c('#B4D0C7','#82B0A2', '#619B8A', '#568A7B'))), 
  xlab="Brain Age Gap", ylab="Density", legend.title = "Youth-Report PDS")  +
  theme(text = element_text(size = 24))

@@

#Parent-Report Puberty
ggpar((categorical_pds_followup %>% 
  filter(!is.na(parent_pds_cat)) %>% 
ggdensity(x = "corrected_gap", color= "parent_pds_cat", fill= "parent_pds_cat", add="mean", palette=c('#B4D0C7','#82B0A2', '#619B8A', '#568A7B'))), 
  xlab="Brain Age Gap", ylab="Density", legend.title = "Parent-Report PDS")  +
  theme(text = element_text(size = 24))

ggsave(filename="followup_parent_pds_mod1.png",
                          width=7, height=4, units='in', dpi=300)
```

@@

ggplot(abcd_brainage_baseline, aes(x=truth, y=corrected_pred)) + 
  geom_jitter(color="#E76F51")+
  geom_abline(a=0, b=1, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Predicted Age", title = "Age v Pred Age - Model 2 (Baseline)") +
  theme_classic() + 
  theme(text = element_text(size = 22))  
ggsave(filename="baseline_truth_corrected_pred_mod2.png",
                          width=7, height=4, units='in', dpi=300)

# Age Bias - truth vs corrected gap
ggplot(abcd_brainage_baseline, aes(x=truth, y=corrected_gap)) + 
  geom_jitter(color="#E76F51")+
  geom_smooth(method=lm, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Corrected Gap", title = "Age Bias - Model 2 (Baseline)") +
  theme_classic() + 
  theme(text = element_text(size = 22))  
ggsave(filename="baseline_truth_corrected_gap_mod2.png",
                          width=7, height=4, units='in', dpi=300)

@@

vip package
```{r}
# Calculate variables of importance
abcd_vi <- vi(abcd_model_5_9) #xgb_final_mod, xgboost_abcd_brain_age_mod
abcd_vi

abcd_vi <- vi(abcd_model_59) #xgb_final_mod, xgboost_abcd_brain_age_mod
abcd_vi

xgboost::xgb.importance(model=abcd_model_5_9)

@@

@@

brain_regions(dk)
brain_labels(dk)

brain_labels(aseg)

ggseg(abcd_vi)

#Actually plot
#Cortical
abcd_vi %>%
  ggplot() +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = Importance))
#Subcortical
abcd_vi %>%
  ggplot() +
  geom_brain(atlas = aseg, 
             position = position_brain(hemi ~ side),
             aes(fill = Importance))
```

@@

#Youth-report puberty
ggpar((abcd_baseline_categorical_pds %>% 
  filter(!is.na(youth_pds_cat)) %>% 
  ggdensity(x = "corrected_gap", color= "youth_pds_cat", fill= "youth_pds_cat", add="mean", palette=c('#FCCA46','#F3B5A5', '#E76F51', '#B43718'))), 
  xlab="Brain Age Gap", ylab="Density", legend.title = "Youth-Report PDS")  +
  theme(text = element_text(size = 24))

@@

#Parent-Report Puberty
ggpar((abcd_baseline_categorical_pds %>% 
  filter(!is.na(parent_pds_cat)) %>% 
ggdensity(x = "corrected_gap", color= "parent_pds_cat", fill= "parent_pds_cat", add="mean", palette=c('#FCCA46','#F3B5A5', '#E76F51', '#B43718'))), 
  xlab="Brain Age Gap", ylab="Density", legend.title = "Parent-Report PDS")  +
  theme(text = element_text(size = 24)) 
ggsave(filename="baseline_parent_pds_mod2.png",
                          width=7, height=4, units='in', dpi=300)

@@

#Cognition Quartiles
ggpar((abcd_baseline_categorical_pds %>% 
  filter(!is.na(cog_quart) & cog_quart!="25-50" & cog_quart!="50-75" ) %>% 
  ggdensity(x = "corrected_gap", color= "cog_quart", fill="cog_quart", add="mean", palette = c('#FCCA46',
 '#E76F51'))), xlab="Brain Age Gap", ylab="Density", legend.title = "Cognition (Quartiles)")  +
  theme(text = element_text(size = 24)) 
ggsave(filename="baseline_cognition_mod2.png",
                          width=7, height=4, units='in', dpi=300)

>>>>

3 plots: youth-report puberty, parent-report puberty, cognition
```{r}

#make categorical variable for puberty
#age-corrected cognition: These are presented as Standard Scores (mean=100, SD=15).
categorical_pds_baseline <-  brainage_pds_baseline %>% 
  mutate(youth_pds_cat=cut(youth_mean, breaks=c(-Inf, 1, 2, 3, Inf), labels=c("1","2","3", "4")),
         parent_pds_cat=cut(parent_mean, breaks=c(-Inf, 1, 2, 3, Inf), labels=c("1","2","3", "4")),
         cognition_cat=cut(nihtbx_totalcomp_uncorrected, breaks=c(-Inf, 85, 115, Inf), labels=c(">-1", "-1-1", ">1")),
         cognition_cat_small=cut(nihtbx_totalcomp_uncorrected, breaks=c(-Inf, 92, 108, Inf), labels=c(">-.5", "-.5-.5", ">.5")),
         cog_quart = cut(nihtbx_totalcomp_uncorrected, quantile(nihtbx_totalcomp_uncorrected, na.rm=T), labels=c("0-25", "25-50", "50-75", "75-100")))
#don't z-score, include more than 1 standard deviation and less than 1 standard deviation (ignore within 1 SD)

#Youth-Report Puberty
youth_pds_baseline_mod1_plot <- ggpar((categorical_pds_baseline %>% 
  filter(!is.na(youth_pds_cat)) %>% 
  ggdensity(x = "corrected_gap", color= "youth_pds_cat", fill= "youth_pds_cat", add="mean", palette = c('#3E502A','#7CA352','#A1C181', '#CCDDBB'))),  #,'#526D37'
  xlab="Brain Age Gap", ylab="Density", legend.title = "Youth-Report PDS", font.legend = 8) +
  theme(text = element_text(size = 12)) 
ggsave(filename="baseline_youth_pds_mod1.png",
                          width=7, height=4, units='in', dpi=300)

#Parent-Report Puberty
parent_pds_baseline_mod1_plot <- ggpar((categorical_pds_baseline %>% 
  filter(!is.na(parent_pds_cat)) %>% 
ggdensity(x = "corrected_gap", color= "parent_pds_cat", fill= "parent_pds_cat", add="mean", palette = c('#3E502A','#7CA352','#A1C181', '#CCDDBB'))), 
  xlab="Brain Age Gap", ylab="Density", legend.title = "Parent-Report PDS", font.legend = 8) +
  theme(text = element_text(size = 12)) 
ggsave(filename="baseline_parent_pds_mod1.png",
                          width=7, height=4, units='in', dpi=300)

@@

#Cognition Quartiles
cog_baseline_mod1_plot <- ggpar((categorical_pds_baseline %>% 
  filter(!is.na(cog_quart) & cog_quart!="25-50" & cog_quart!="50-75" ) %>% 
  ggdensity(x = "corrected_gap", color= "cog_quart", fill="cog_quart", add="mean", palette = c('#7CA352',
 '#CCDDBB'))), xlab="Brain Age Gap", ylab="Density", legend.title = "Cognition (Quartiles)", font.legend = 8)  +
  theme(text = element_text(size = 12))

ggsave(filename="baseline_cognition_mod1.png",
                          width=7, height=4, units='in', dpi=300)

ggarrange(youth_pds_baseline_mod1_plot, parent_pds_baseline_mod1_plot, cog_baseline_mod1_plot, 
          labels = c("A", "B", "C"),
          ncol = 2, nrow = 2)

ggsave(filename = "distributions_baseline_mod1.png",
                          width=7, height=5, units='in', dpi=300)

@@

baseline_pred_mod1_plot <- ggplot(brainage_pds_baseline, aes(x=truth, y=corrected_pred)) + 
  geom_jitter(color="#A1C181")+
  geom_abline(a=0, b=1, color='#233D4D') +
  #geom_smooth(method=lm, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Predicted Age") +
  theme_classic() + 
  theme(text = element_text(size = 14))  
ggsave(filename="baseline_truth_corrected_pred_mod1.png",
                          width=7, height=4, units='in', dpi=300)

@@

baseline_gap_mod1_plot <- ggplot(brainage_pds_baseline, aes(x=truth, y=corrected_gap)) + 
  geom_jitter(color="#A1C181")+
  geom_smooth(method=lm, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Corrected Gap") +
  theme_classic() + 
  theme(text = element_text(size = 14))  
ggsave(filename="baseline_truth_corrected_gap_mod1.png",
                          width=7, height=4, units='in', dpi=300)

ggarrange(baseline_pred_mod1_plot, baseline_gap_mod1_plot, 
          labels = c("A", "B"),
          ncol = 2, nrow = 1)

ggsave(filename = "pred_bias_baseline_mod1.png",
                          width=10, height=5, units='in', dpi=300)
```

@@

followup_pred_mod1_plot <- ggplot(brainage_pds_followup, aes(x=truth, y=corrected_pred)) + 
  geom_jitter(color="#619B8A")+
  geom_abline(a=0, b=1, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Predicted Age") +
  theme_classic() + 
  theme(text = element_text(size = 14))  
ggsave(filename="followup_truth_corrected_pred_mod1.png",
                          width=7, height=4, units='in', dpi=300)

# Age Bias - truth vs corrected gap
followup_gap_mod1_plot <- ggplot(brainage_pds_followup, aes(x=truth, y=corrected_gap)) + 
  geom_jitter(color="#619B8A")+
  geom_smooth(method=lm, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Corrected Gap") +
  theme_classic() + 
  theme(text = element_text(size = 14))  
ggsave(filename="followup_truth_corrected_gap_mod1.png",
                          width=7, height=4, units='in', dpi=300)

@@

#Panel Plots
ggarrange(baseline_pred_mod1_plot, baseline_gap_mod1_plot, followup_pred_mod1_plot, followup_gap_mod1_plot, 
          labels = c("A", "B", "C", "D"),
          ncol = 2, nrow = 2)

ggsave(filename = "pred_bias_mod1.png",
                          width=10, height=10, units='in', dpi=300)

@@

youth_pds_followup_mod1_plot <- ggpar((categorical_pds_followup %>% 
  filter(!is.na(youth_pds_cat)) %>% 
  ggdensity(x = "corrected_gap", color= "youth_pds_cat", fill= "youth_pds_cat", add="mean", palette=c('#B4D0C7','#82B0A2', '#619B8A', '#568A7B'))), 
  xlab="Brain Age Gap", ylab="Density", legend.title = "Youth-Report PDS", font.legend=8)  +
  theme(text = element_text(size = 12))

@@

#Parent-Report Puberty
parent_pds_followup_mod1_plot <-ggpar((categorical_pds_followup %>% 
  filter(!is.na(parent_pds_cat)) %>% 
ggdensity(x = "corrected_gap", color= "parent_pds_cat", fill= "parent_pds_cat", add="mean", palette=c('#B4D0C7','#82B0A2', '#619B8A', '#568A7B'))), 
  xlab="Brain Age Gap", ylab="Density", legend.title = "Parent-Report PDS", font.legend=8)  +
  theme(text = element_text(size = 12))

ggsave(filename="followup_parent_pds_mod1.png",
                          width=7, height=4, units='in', dpi=300)

ggarrange(youth_pds_followup_mod1_plot, parent_pds_followup_mod1_plot, 
          labels = c("A", "B"),
          ncol = 2, nrow = 1)
ggsave(filename = "distributions_followup_mod1.png",
                          width=10, height=4, units='in', dpi=300)

@@

baseline_pred_mod2_plot <- ggplot(abcd_brainage_baseline, aes(x=truth, y=corrected_pred)) + 
  geom_jitter(color="#E76F51")+
  geom_abline(a=0, b=1, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Predicted Age") +
  theme_classic() + 
  theme(text = element_text(size = 12))  
ggsave(filename="baseline_truth_corrected_pred_mod2.png",
                          width=7, height=4, units='in', dpi=300)

# Age Bias - truth vs corrected gap
baseline_gap_mod2_plot <- ggplot(abcd_brainage_baseline, aes(x=truth, y=corrected_gap)) + 
  geom_jitter(color="#E76F51")+
  geom_smooth(method=lm, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Corrected Gap") +
  theme_classic() + 
  theme(text = element_text(size = 12))  
ggsave(filename="baseline_truth_corrected_gap_mod2.png",
                          width=7, height=4, units='in', dpi=300)

#Panel Plots
ggarrange(baseline_pred_mod2_plot, baseline_gap_mod2_plot,
          labels = c("A", "B"),
          ncol = 2, nrow = 1)

ggsave(filename = "pred_bias_mod2.png",
                          width=10, height=5, units='in', dpi=300)

@@

vip package
```{r}
# Calculate variables of importance
#abcd_vi <- vi(abcd_model_5_9) #xgb_final_mod, xgboost_abcd_brain_age_mod
#abcd_vi

#abcd_vi <- vi(abcd_model_59) #xgb_final_mod, xgboost_abcd_brain_age_mod
#abcd_vi

#xgboost::xgb.importance(model=abcd_brainage_model)
#xgboost::xgb.importance(model=abcd_vi)

abcd_brainage_model <- rio::import("/Volumes/devbrainlab/Lucy/BrainAGE/fyp/xgboost_abcd_brain_age_mod_5_9.rds")

#This works!
#abcd_vi <- vi(abcd_brainage_model) #xgb_final_mod, xgboost_abcd_brain_age_mod
#abcd_vi
#write_csv(abcd_vi, "abcd_vi.csv")

@@

vip(abcd_brainage_model, num_features = 20)
ggsave(filename="abcd_model_vip.png",
                          width=7, height=4, units='in', dpi=300)

@@

abcd_vi_renamed <- rio::import("~/Documents/FYP/abcd_vi_renamed.csv")
abcd_vi_renamed_dk <- rio::import("~/Documents/FYP/abcd_vi_renamed_dk.csv")

#check labels
brain_labels(dk)
brain_labels(aseg)

#Cortical - Volume
dk_vi_vol <- abcd_vi_renamed_dk %>%
  filter(grepl('Vol', Variable)) %>% 
  filter(label != "") %>% 
  select(Importance,label)

dk_vi_vol <- data.frame(dk_vi_vol)

ggplot(dk_vi_vol) +
  geom_brain(atlas = dk, position = position_brain(hemi ~ side), aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51') +
  labs(title = "Cortical Volume")
ggsave(filename="abcd_model_dk_vol_importance.png",
                         width=8, height=4, units='in', dpi=300)

#Cortical - Area
dk_vi_area <- abcd_vi_renamed_dk %>%
  filter(grepl('Area', Variable)) %>% 
  filter(label != "") %>% 
  select(Importance,label)

dk_vi_area <- data.frame(dk_vi_area)

ggplot(dk_vi_area) +
  geom_brain(atlas = dk, position = position_brain(hemi ~ side), aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51') +
  labs(title = "Cortical Area")
ggsave(filename="abcd_model_dk_area_importance.png",
                         width=8, height=4, units='in', dpi=300)

#Subcortical
aseg_vi <- abcd_vi_renamed %>%
  filter(label != "") %>% 
  select(Importance,label)

aseg_vi <- data.frame(aseg_vi)

ggplot(aseg_vi) +
  geom_brain(atlas = aseg, side="coronal", aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51')
ggsave(filename="abcd_model_aseg_importance_coronal.png",
                          width=7, height=4, units='in', dpi=300)

ggplot(aseg_vi) +
  geom_brain(atlas = aseg, side="sagittal", aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51')
ggsave(filename="abcd_model_aseg_importance_sagittal.png",
                          width=7, height=4, units='in', dpi=300)

#troubleshooting names
aseg_labs <- brain_labels(aseg) |> 
  as.character()
aseg_vi$label[!aseg_vi$label %in% aseg_labs]
aseg_labs[!aseg_labs %in% aseg_vi$label]

dk_labs <- brain_labels(dk) |> 
  as.character()
dk_vi_area$label[!dk_vi_area$label %in% dk_labs]
dk_vi_vol$label[!dk_vi_vol$label %in% dk_labs]

dk_labs[!dk_labs %in% dk_vi_area$label]
dk_labs[!dk_labs %in% dk_vi_vol$label]

#'#FCCA46','#F3B5A5', '#E76F51', '#B43718'
```

@@

#Youth-report puberty
youth_pds_baseline_mod2_plot <- ggpar((abcd_baseline_categorical_pds %>% 
  filter(!is.na(youth_pds_cat)) %>% 
  ggdensity(x = "corrected_gap", color= "youth_pds_cat", fill= "youth_pds_cat", add="mean", palette=c('#FCCA46','#F3B5A5', '#E76F51', '#B43718'))), 
  xlab="Brain Age Gap", ylab="Density", legend.title = "Youth-Report PDS",  font.legend = 8)  +
  theme(text = element_text(size = 12))

@@

#Parent-Report Puberty
parent_pds_baseline_mod2_plot <- ggpar((abcd_baseline_categorical_pds %>% 
  filter(!is.na(parent_pds_cat)) %>% 
ggdensity(x = "corrected_gap", color= "parent_pds_cat", fill= "parent_pds_cat", add="mean", palette=c('#FCCA46','#F3B5A5', '#E76F51', '#B43718'))), 
  xlab="Brain Age Gap", ylab="Density", legend.title = "Parent-Report PDS", font.legend = 8)  +
  theme(text = element_text(size = 12))

ggsave(filename="baseline_parent_pds_mod2.png",
                          width=7, height=4, units='in', dpi=300)

@@

#Cognition Quartiles
cog_baseline_mod2_plot <- ggpar((abcd_baseline_categorical_pds %>% 
  filter(!is.na(cog_quart) & cog_quart!="25-50" & cog_quart!="50-75" ) %>% 
  ggdensity(x = "corrected_gap", color= "cog_quart", fill="cog_quart", add="mean", palette = c('#FCCA46',
 '#E76F51'))), xlab="Brain Age Gap", ylab="Density", legend.title = "Cognition (Quartiles)", font.legend = 8)  +
  theme(text = element_text(size = 12))

ggsave(filename="baseline_cognition_mod2.png",
                          width=7, height=4, units='in', dpi=300)

ggarrange(youth_pds_baseline_mod2_plot, parent_pds_baseline_mod2_plot, cog_baseline_mod2_plot, 
          labels = c("A", "B", "C"),
          ncol = 2, nrow = 2)
ggsave(filename = "distributions_baseline_mod2.png",
                          width=7, height=5, units='in', dpi=300)
```
